..Theft shall not be tolerated*

Notes 1
Martin Baroody


Mathematics, logic, reality - Isomorphism, homo; triangles. Homomorphism concept is isomorphic to equilateral triangle… are all isomorphisms just hidden homomorphisms? Homomorphism and isomorphism as a tree structure (what is the root? How interchangeable is the root? How unified is everything, how many separate graphs and interactions exist? Link perhaps to dimension in Lin alg? Can these different objects be oisomorphed unto each other? Distinction between object and interaction, or can we view intersxtion as object, and vice versa? God as root… or not… God is SUPERIOR? Axioms. Different objects. Stretching an object as an isomorphism, involves different views of what comsitutes isomorphism? An initial state) , isomorphism as outward edges. ***

Game theory

Mathematics - Combining mathematical objects into “space” **

Lifestyle, intelligence - Undeserved yet informative obs vs pure intellect

Biology, evolution, neuroscience, physics - Dopamine peaks, troughs, motivation, addiction, peak reduction, acceleration, discontent with stasis or constant velocity (inertia)

Psychology - People categorize poorly understood societal concepts into box with negative connotation, but they make sure to avoid concepts of pitied (they want to be the pitied ones, victims). Pity as positive

Piano ad

Psychology, power, society - Leaders, their incitations to stupid questions/responses/comments, avoid this mode

Physics, mathematics - Can acceleration be inertial frame? Can we know? (Connection to Lin Alg, manifolds) relativity ***

History, intelligence - Leo
Philosophy, aesthetics, lifestyle - Math so that we don’t get lost in art, art so that we may love the math. Art and math as yin and Yang, unproveable jerking and desecrating a beautiful tree for its planks, psychopathy, abridging both artistically and mathematically, impatience as window to hidden values and intentions (also Leo’s goal, dopamine, motivation, vs rigid hidden naive ideals like karate). Application to social interaction: good balance is neither pure math nor pure art. There is math (reality, principles) in art, whether “evolutionary” or otherwise, we cannot say reality is subjective due to the presence of the few schizophrenics and mentally incapacitated folks, same with art, artistic quotient ***
Psychology, reality - Eye window to soul, where do we look, and for what, and for how long? Science. Observation. Keep deviation from reality in check. True love of nature vs arrogant delusional selfishness.
Psychology, lifestyle, neuroscience - Lack of love as motivation, neuroscience. Satisfaction ends the drive.
Society, psychology - Rally against the uncreative, who hate  creativity and love the norm. Normal people will read this and scoff at how the world back then was so close minded, will link in “idiotic” religion etc, without realizing that the concept is universal and holds today and holds for them. Can represent with state machine perhaps, of reading endlessly

Lifestyle, reality - Life as direction of energy, why go against natural energy transfer, ride it and harness it instead

Mathematics, AI, probability - Extended form game, recurrence/seq, link to Bayesian updating, amount of true unpredictability vs salient probability (A), involving out of the box info in the sequence such as seq over several games or over players, though this is exploitable in itself perhaps (be aware of own exploitability and fit that into a Bayesian distribution of its own), neural network policy as “stateless” and possible disadvantages of such formulation if any (for example, high potential for bad or inefficient optimization)

AI, mathematics - Nonlinear landscape carved incompletely (or perhaps misleadingly) by training data, uncertainty dynamics, probability of hill properties, more exploration, let large chunk of  training data define landscape (partially) to explore (avoid minibatches), sample variety of hills, treat each as own convex  optimization landscape.

Lifestyle, reality, probability - Get better at thinking about poker; discipline , don’t deviate from real probability of things, and don’t ignore unfolding of a (perhaps once improbable) realization

Philosophy, mathematics - Inefficiency: in some way, the same distance (or position by some view) is covered more than once

Music, reality, AI, project - Music components — refine. Allow user to progressively edit a realization. Map “music” components to emotional or artistic jargon, in both ways. Allow user to add, remove etc. aleatory. Refinement possible. Perhaps always (limit point)

Psychology - Sis — “who were you with?” -> you don’t know -> WAS IT A GUY? ->yes -> what’s his name? -> Eric — reveals info to not appear guilty of the obviously false charge. Interesting tactic. “Guy” better than “girl” here as it is far less jarring and accusatory (good in long run for social relationship, and perhaps in moment, definitely in medium term of this interaction)

Logic, reality, mathematics - Godel Escher Bach lecture 1 on YouTube, write about

Aesthetics, reality - Art reflecting universe, love “hidden” immense complexity in parsimonious artwork

Aesthetics, lifestyle - Baby as illustration of inherent aesthetic reality, pure reason: just developmental stage. But there is a beauty to it. Why deny or remove it? (Link to exploitability Va psychopathy, psychopathy as equilibrium, but for what end?)

Logic, religion, mathematics - Faith, gum ball machine (math evidence), logic and truth and probability and knowledge (belief/disbelief), science, initial assumptions, Gödel

Mathematics - Calculating area of a circle, pi, approximations

Evolution, music - Speech and music, prehistorical/evolutionary explanations at different scales (tonic differences in scales, relationships between notes and their effect, trajectory of song)

Aesthetics - Visual art vs photography, art as creation and realization, emphasis, complexity of universe, relatively unbounded by time (history) or natural chance

Probability, AI - Probability distributions and scale; especially over finite horizon rather than expected value’s infinite samples, imagine 3 trials with 90% probability of +5 and 10% probability of -70 vs 100% chance of +1… (examples like this)

AI - RL policies as states in themselves… meta RL?  RL on RL?

Project - Lebanon opportunities

Psychology, lifestyle, society - “Not reacting”, “dull” -> “what’s wrong with you”, made fun of, then “what’s wrong” twice… how to respond? Must fake some social energy; look around, adapt to “normality” to extent

Lifestyle - No music today; when reinstantiated put restrictions on time (~15 mins) and proximity (~2 hours) to be withheld for the day

Mathematics - Axioms as “basis” for mathematical system

Lifestyle, history, literature - “My True Glory”. Alexander the Great’s manifestation of this.

Lifestyle, morality, religion - Iterative goodness, can always be maintained at any point; free will

Music, reality - Leibniz: “music as joy of counting”, innate love of universe and math

Music - Similarities between Mozart, Beethoven (I.e. Mozart SQ18 -> Beethoven SQ14; mvt3 vs mvt4, mvt4 vs mvt6)

Music - Recurring thematic material in the same composition (Bach prelude and fugue, Mozart sq’s, concertos, etc; piano sonatas)

Music - Harpsichord as better conduit of counterpoint, piano as better vessel for romanticism

Philosophy, literature - The Republic — Socrates is clearly a genius, but a lot of arguments rely on a “frame” or “lens” (degree of subjective twisting x, with leeway for alternate frames) rather than an absolute, irrefutable  truth. For example, in discussion w Polemarchus, framing justice as a specific skill/art/practice akin/on the save level as medicine, cooking, etc. in order to show that his def of justice (doing right to friends and wrong to enemies, ie reflecting perceived energy) will lead to an absurdity of justice as a practice being useless (would defer to someone skilled in any application of justice, only useful for the art of safeguarding things, in which case just men are also the experts of stealing them, making them unideal for those jobs too). But this assumes justice on the same level and concept as other arts rather than a thread through all of them, involves a concept of “use” of justice, and the idea that the just man would/could be unjust (which relies on the idea that masters of an art in terms of “creation” are also the experts of the destructive side of that coin), all of which are very debatable/perhaps untrue frames that should not be immediately accepted. Such is the danger of being the one-sided subject of Socratic questioning. But in the end relates similar concept of being ideally just entailing being an expert at harming people (enemies). Argument about erring in such judgements of good and evil, very good point, beware of perception based applications. “Bad friends” argument (very interesting argument, link to forgiveness in Christianity; this view of justice views people as static bad and good and our own perception as correct, about ourselves and others, all naïve). Understanding of who is bad person, what if they did no harm to us, show us “signs of goodness”, but injure other people; involves subjectivity. To harm enemies means to injure them and make them further unjust, and the world unjust (literally), goes against concept of justice (note this only applied if all men are of equal substance like Socrates says).

Philosophy - Kant Critique of Pure Reason
Reason, link to linear algebra vector spaces; pure reason as holding beyond any lens, Maxim holding for particular lens, desire, end etc. but not universal, maxims in subspace of pure reason (leeway) as family
Categorical imperative as condition of will despite any situation or state category; inherent parametrization for “continuous” world, or exhaustive “if” conditions in case of disjointness in domain, in which case there is the possible angle of “maxim” but determined non-ambiguously
Christ sets desires straight

Project, AI - AI community of language learners, but their own language. Compressed atomic vocabulary.

Music - Beethoven sonata 32 - first movement Tritones, intense and dark, ends on “immense possibility of positivity”, next movement as affirmation of such. Transcendence of pain. Progressively more movement, dancing with life.

Philosophy - Republic
Socrates manages to subdue and debate Thracymacus by making him feel superior in the beginning, giving him leeway to show off without any perception of intellectual threats, animosity, or opposing force (Socrates puts on a front of weakness). Even initial suspicions and resistance to original replies by Socrates are nullified as Socrates keeps up the act. But puts in enough opposition (second reply by Socrates) to not be completely disrespected as to not be debated against by Thracymachus. Walks a good line, shows enough opposition, with enough weakness, for Thracymachus to perceive debating as a good idea, to not look weak, arrogant, or unwise (if he does not debate Socrates his big words are clearly empty and aggression uncalled for, especially with Socrates going against him a bit) and to perceive himself as being easily able to win (Socrates claiming he knows nothing). Socrates also claims he might default to one of the answers Thracymachus initially barred, so Thracymachus feels obliged and emboldened to give his opposing opinion, which he insinuated he had in the beginning. When Thracymachus resists answering again, claiming Socrates will play the old game of questioning, Socrates feigns his own stupidity and lack of knowledge of the answer (“what else can you expect?”) and taunts Thracymachus looping in the direction in which he is clearly going (“the answer should naturally come from you…”) framing it as either I answer or you answer, in which case there is a clear answer and Socrates has “logically shown” leeway to sit back and question (but framed as Thracymachus giving his definition, of course).
Gives definition of interest of stronger
Socrates requests definitions, which is good idea. “Stronger”, and meaning of “interest”.
T: I  wonder about the psychology of Thrasymachus. Clearly supports his idea of stronger party defining “justice”, perhaps models himself after such rulers, and uses this as credence for imposing his own will, whether or not it is agreed upon as just by others (for example, dominance, selfishness, literal injustice…)
T: general point of justice as equated to some law written by humans. Link to Christianity, and idea of morality going beyond “a set of rules”, and also to Kant (perhaps the rules have inherent contradictions in certain scenarios, disqualifying them as categorical imperatives). Justice is meant to convey some true moral, and actions according to the balance of that moral in the world/situation. The truth is not conditional, so justice should not involve a conditional will/desire (maxim) that contradicts itself in its own current state or through the passage of time. Thrasymachus is clearly twisting the definition of justice here beyond its meaning
Socrates: “we must find out whether your definition is true”… interesting. Good frame. Clearly implies that the definition is not an axiom which cannot be proved or disproved.
Finds contradictions. (Men in power can be irrational, make bad rules, against their own interest due to their lack of foresight - clear ambiguity in the term “interest” and a can of worms in itself, so obeying them is unjust, contradiction). Human irrationality is a common debating point here and for Polymarchus, perhaps more emphasis on “ideal” is necessary to get to anything meaningful
The opposition needs to backtrack to get out of the tangle of contradiction; they need to now claim that the weaker subjects need only do what the ruler believes to be in their best interest (meaning exactly what they command). Which is a more absurd definition than before.
Thracymachus further claims “stronger” is better and may make small errors “locally” but eventually corrects them and is successful in their craft, craftsmen do not make mistakes until their knowledge fails them, and rulers can be considered craftsmen. Then, what if a ruler orders around another craftsman or goes against their recommendation? If the ruler is “mistaken”, how can we know if we are always to assume they’ll be right in the end?  Shifts his position further to include “stronger” man to be most capable, without making mistakes, tightening the definition greatly to the point of absurdity. How could any other perceiver know that the man in power is the “strongest”; and or identify any individual at all as “stronger”?
Socrates makes point about art/craft as having for interest its own subject matter (make clear the definition of interest). Thus a perfect practitioner of any art would do what is best for its subject matter (who is weaker, and subject to the craftsman’s work). Thus, these arts are concerned chiefly with the (weaker) subject, with the “perfect” ruler as no exception. We now get a contradiction or infinite loop with the interest of the stronger being the interest of the weaker.
T: I wonder if there is some relation to Thrasymachus’ next utilitarian tirade, which flips morality and praises pure utilitarianism over virtue which only ends in pitiless pain; and Nietzsche’s views
Thrasy views art as means to an end (power?); justice as “defined by some authority for his own gain and the loss of the weaker”. Justice as always bring a disadvantaged position compared to injustice, especially since justice does not tend to plan ahead à la Machiavellianism (ie. a contract)
T: but makes you wonder by what metric “advantage/disadvantage” is defined (think about the long term, what really matters) and if even by the “power metrics” injustice pays off as much as we think it does
Distinction between “law of man” (direct rules governing states and contexts) and “moral law”, psychology: people think of you as vile for breaking such rules, even when your actions clearly do not conflict (or even uphold) the moral law; communication is key
Goodness as implying action, thus a drive, ambition as “wrong”, drive as “being compelled” divinely?
Socrates makes point on weakness vs strength as an analogy to arts; the artist practices his art for the hood of another party (weaker) but also cannot/does not work for nothing (conferring advantage without receiving; artist as weak). This is mediated through pay (artist receives benefit, is no longer “weaker”) but this is a different art than the original art of the artist. “Receiving” would indicate an initial weakness.
Thracymachus makes association between strength, goodness, wisdom, etc (it is debatable whether ANY of these are really analogous…) then the “unjust” want to have more than both the just and the unjust (their likeness) whereas the just only want more than the unjust, that they may further the cause of justice. Socrates shows that it is better for a wise person to want to gain more than his unlike or opposite (who has skills and knowledge or any analogue that he does not have). Makes case of musician, two musicians (with different subskills) wouldn’t consider the other lesser, but would consider themselves (in this simplified domain of comparison) greater than any non musician. Will probably make an isomorphism to justice. Raises a question though of what can be classified as an “overarching art” (this argument implies a hierarchy of arts) and knowledge of everyone’s position in the umbrella. I know this is a proof by contradiction so this is not needed for this sake yet but we would clearly need to know what constitutes justice so that the just may perceive it’s likeness and unlikeness.
T: another possible argument here is that the unjust ends up having no real allies, since they are going against their likeness, which is an immense disadvantage, and contrary to Thracymachus’ pitch. It is clearly not wise either. And if we assume further that the strong are all unjust it gets even worse, having to fend off all these strong enemies as well as the unified just men
Socrates makes link with chaos and order; that power cannot be well exercised without justice (are there subsets of “tenets of justice” that are more potent than the whole thing?)
As I was saying before, Socrates makes the link between justice and unity and injustice with being attacked on all sides which is no way to live well. Without justice there is no “unified state” as all fronts are open to attack and will be attacked due to the festering of injustice. A party can do nothing when there is brutal infighting and constant suspicion. Harmony is much better
T: how far can we extend the concept of harmony? Link to discipline in everyday life? Can discipline exist without pain, by some lens?
T: can make a counter argument using “smart psychopath”; who can appear and act just when convenient, but can/will do away with such notions when convenient. Then this is not for the good of the group, however, and the psychopath’s intentions and desires are very far against the just man’s. In fact it is a disadvantage in this frame due to constant faking, which is difficult to uphold, and the attack from the unified just men when the truth is laid bare. Psychopath always has to work around the concepts of justice (never contravening them too blatantly) and act against it with the greatest of discretion and planning. Almost impossible to uphold. Whereas for just men everything remains natural. It is a better existence. Psychopathy festers better when injustice festers in society (the west). Would be also very interesting to wonder how to act in a GIVEN condition such as a society where injustice and irrationality fester (the west, perhaps all of them to some degree). This currently deals with an IDEAL condition.
Makes a case of “united power” as only half-evil for they were civil/just enough to unite. Really raises questions of what is good/evil. But right now we can get away with describing half evil. Perhaps by this mechanism we can get to a concept of goodness as well. Note a link between disorganization due to evil and pure chaos/yin; rendering it ineffective and crippled by chaos. I wonder if “pure goodness” would also be inhibitive here? Not if pure goodness is different from “pure order/yang”, which I believe it is.
Also raises question of “what matters”. Though is guess here the point is of contradiction, clearly it is shown that injustice collapses on itself; it implies a certain “desire” or frame of what matters (power, glory, material gain, selfishness) yet cannot achieve it. Justice clearly does not operate in the same space but we must ask which space it operates in

Machine learning - reading TRPO paper, value function of state, and choosing next state according to higher advantage, is akin to getting closer to a goal; purging bad possibilities is akin to getting closer and closer to the right place (interesting analogy, lower distance -> less leeway), and also increases advantage, due to less possibility of bad states and more possibilities or opportunity of good states.

religion, morality, society, lifestyle - (good and just) civilization as enabler of true goodness and virtue? Meaning of good civilization/society, ideal initial education, goal that people follow through by free will, how to deal with evil/corruption, analogy across many levels of being (individual, group, society, inter-civilization relations)

Philosophy, lifestyle, music - link (seen in Bach, Mozart progressions) between beauty/transcendence/love and joy, and seriousness/resolution/affirmation/ profundity/satisfaction, circular chain of effect

Religion - story of Cain and Abel; Abel as having pure passion and love, while Cain is halfheartedly “good at his job”, similar to intellectual great at math/science, vs. Other scientist who may be less intelligent but has true love of nature, the world, God, and offers his devotion to help the world and serve God although perhaps the smart guy could come up with better ideas for a given problem

Philosophy - Socrates “I know nothing” - preemptive of philosophy of science; can disprove things with high conviction, but knowing the actual fabric of reality is literally infinitely more difficult. Infinite configurations by which any set of observations can hold true, can only disprove with more information/corrections, but still despite the pruning it is very difficult to boil down to the exact truth, plus some things are unobservable. Socrates tends to give a lot of counter arguments and proofs by contradiction, which aligns closely with this spirit

Lifestyle - split day into 3 — learning, acting, appreciating


Religion - John 20:29 - blessed are they that have not seen, yet have believed.
This is a good lens. Faith over all things
John 21:12 - none of the disciples durst ask him, who art thou? Knowing that it was the Lord
Often I feel this. Knowledge without necessarily needing the mathematical perfection of a proof. Proof is to convince yourself of something that you do not already have strong faith in. Faith in Christ is immediate. To need to prove to believe is to have no faith, is to have more faith in the world, induces a frame of doubt
John 21:22 - if I will that he tarry on till I come, what is that to thee? Follow thou me
Focus not on evil or on betrayal/pain/revenge or fear, but always on the Lord who overcomes all these things

Machine learning, mathematics - TRPO paper, there is a proof involving a comparison between a more ideal loss function (expected return) and an approximation, the proof shows a first order similarity; that both the function and its derivative are equal upon equal parameter settings, thus the loss landscape is similar at all points, and is thus a similar optimization landscape at all points as well as for small neighborhoods around that point
I wonder if we can do proofs where instead of checking for first order equality, we check for “landscape equality” to some order. For example if the gradient points in a similar direction

History, lifestyle - da Vinci - solitude, countryside, being your own master 
Comparison to Alberti, who was open hearted and communal, grilled people from all walks of life to understand the secrets of their art/good qualities (this is a good thing to do), but also believed in public discourse and idea dissemination, advancing science, etc; whereas Leonardo was not so interested, kept a lot of ideas private (perhaps the mass of stubborn parrots of already published books contributed to this)
Alberti was very outwardly graceful; in walking, and in speech; that they are artistic. Leonardo emulated this. So will I
Todo: practice speech

Todo: art, drawing, experiment

Lifestyle - Aurelius Meditations
Righteousness for its own sake, governed by rationality, in all things
Appreciation (even of enemies/tyrants), forgiveness, lack of strong affectation/passion (I think I disagree to an extent). Love of humanity and friends
To live nobly
Not allow emotional deviance, to always remain the same even through pain or temptation

Lifestyle - immerse yourself only in good things, like a renaissance workshop

Art - importance of shape (ie curls of hair), small details (ie configuration of body and veins) and their relationship with the other details of the artwork, movement, viscerality

Art - photographs as “initial scene/model” for later drawings

Machine learning - use chatGPT, see how much it can learn through itself (teaching itself. It has all the internet). Keep experiments secret through some type of key that gpt and I both understand but that openAI folk will not, and communicate using this code

Lifestyle - fear -> adrenaline, use as is, as motivator for action, rather than trying to repress etc. go with flow. This is what Goggins does. Opportunity for action/bravery

Music, neuroscience - good music like dopamine process, deviation from baseline, need to return to baseline (progression, movement), gratifying resolution, development as goal in sight. A lot of art, perhaps, emulates this dopamine dynamic between pain, movement, satisfaction
Reflection on such experiences as a thing of its own, provides a deep satisfaction as well, this is also reflected in music


Lifestyle - things are fun, things are good. Buddhism still has an action space except at lowest level of no desire (subspace). Other modes of life as refinement of Buddhism (involve emotional affect as good thing); meditation to get you to such principles, not to be deviated from (one level of dimension above Buddhism subspace)

Lifestyle, mathematics - life as GAN, refinement between normal life (unconsciousness, consciousness) and meditation (higher order consciousness, self reflection and correction, priming and refinement of normal life’s process), is such a formulation mathematically explorable, given some axiom set/parameters of refinement?

Lifestyle, psychology, neuroscience - things spiral, brain seeks known contexts as the actor makes decisions, thus bad habits have a gravitational force that is strong even through seemingly logically innocuous actions that entail a bad association (music). Better to go too disciplined than ti give chance to pleasurable leeway.  Put limits on actions with bad attachments (music), for example time limit/space constraints. Spirals are very bad. Lead to immense wastes of time and negativity. Avoid at all costs.

Neuroscience, lifestyle - dopamine motivational loops defined by a goal. Baseline and relative reward/displeasures created by end goal. Modulate end goal to involve pain and growth rather than fixed strict and naïve objective subject to chaos. Like as da Vinci said, a love of nature and the cosmos and science, rather than love of only glory and victory and dominance by some arbitrary metric.

Mathematics - “everything that I think now is wrong” — logical paradox? Is there always a truth then (according to our system of reality)? Link to Bertrand Russell’s paradoxes. Involves levels of systems. Statements like this are from a bird’s eye view of the system and perhaps are separate in a sense from the system… or are they?

Science, philosophy - ladder of sciences from first principles: physics -> chem -> biology -> neuroscience -> psychology -> social science. Generally gets less predictable/accurate as you go along. But funnily enough complexity also decreases, and specificity increases…. In an ideal world, things would get easier rather than harder, but practically it’s the opposite

Psychology - wealthsimple ad (find on LinkedIn), clearly clever/spectacular, but does it sell? Does it serve its intended purpose (getting people to buy) as well as other more plain ads?

Psychology, neuroscience, lifestyle: sex -> orgasm, depletes motivation, drive, energy. Time sink to getting it back up. Constant releases keep level constantly in check. Motivation sink. Way to prevent men from constantly seeking other mates with their extremely high sex drive, keep family strong and maintain close bond. But depletes passion in things, excitement, drive. Not only for sex but other things. Masturbation is more constant expression of this, but with mo benefits at all, and more availability. End this. Sex drive links to other areas of motivation as a result, and depletion of it depletes drive for other things, leads to bad spiral

Philosophy, lifestyle - mediations Aurelius
“I shall meet with (people with unpleasant traits)…” goes to say that they are of the same seed as him anyway. I’m not sure of this. Mentions that no one of these can fix evil/ugliness onto him. This is a good lens. There is what is good/beautiful and what is evil/ugly. Beauty is infinitely greater. May we always see beauty in all circumstances, to allow others to fix us into ugliness (and they have no real power to do so if we are conscious of our own power of free will) entails absurdity, contradiction, the most irrational suboptimality and self-indiced suffering and weakness and lowliness. May we always look towards goodness and beauty, in all things, ugliness can never compare and others’ ugly rearings have so little weight in comparison
Cannot be mad at kinsmen; if they are of the same “seed”, to be mad at them, hateful/spiteful/vindictive, is to fundamentally hate yourself as well; this is not a good lens through which life should be passed
To act against one another is “contrary to nature” — not entirely true but does hold some truth, people are alive due to cooperation, and love of cooperation is endeared in us

Philosophy, neuroscience - can never escape human nature in some level, humans act according to their structure of arms/legs, brain function, perception limitations and structure, vulnerabilities… humans then can only optimize a certain subclass of functions in an uncountable infinite class of possible functions that could operate in reality, not all of them realized by existing agents but are possible. But is this actually true? Assuming logic and mathematics are well founded, can human intelligence transcend human limitations? (Think of tools, planes, etc) to what extent can limitations be overcome? Intelligence as widening space of agency functions. Is there a limit to which functions can be touched? Are all “real” limitations/problems resolvable?
We do know of one hard limit on intelligence: knowledge of truth, which is impossible. Everything is a theory.
Related: we think of the world as governed by fundamental laws, at least of physics. Could it be possible for a human to change these fundamental laws in some way? Think of using a set of axioms to overcome the limitations of the axioms (a contradiction through logic), is this possible ever, in any system? Think for example of limits and irrational numbers, Q and R, is this applicable? Or even linear algebra, a non-vector space collection of numbers; can use addition of two elements or scalar multiplication to get something not in the set. Must such a process converge to a single set of elements if repeated ad infinitum? Is the universe such an (initially) inconsistent system, in the midst of convergence, or is it already converged? Or if there exists some system which would never converge (think an increasing sequence), could this be applied to the universe, as a system that will never converge? Difference between an “important” change (axiomatic) and non important (isomorphism, consistent). Perhaps a set of axioms that is once true becomes false as the process continues, is that possible? (Interesting cause we can only theorize about axioms)

To read; Xenakis, stochastic music

Music, neuroscience- Xenakis as art, even though it is essentially physical simulations or math/stochastic models in auditory form, it still has an impact on us, despite relatively less human construction (debatable); imagine cavemen on the face of a forest fire or massive wave/tornado/lightning, the sounds of these are immensely arousing even by initial perception (without any aesthetic/romantic processing), very primal/visceral response to immediate danger or important cues in surrounding, and these are sounds of purely physical processes. Imagine Impressionism as a spectrum of romantic attachment to the perception, Debussy would be more on the romantic end, Xenakis on the other; simulations of extreme physical phenomena link to the primordial arousal circuitry and as such lead to an effect. Xenakis constructs them so we’ll that they tap into the intricate sounds of nature

Philosophy, morality - “perfect goodness” is unachievable practically. Everyone is ambivalent about something. No one can do everything good that there is to do. There is always some issue to be solved, some suffering to be alleviated; cannot deal with it all, and sometimes (always) we consciously choose to ignore/not deal with some of it (walking past homeless people). Other people tend to take this the wrong way, especially when involving them as the unhelped; self confidence and faith is needed. This is not contradictory with morality. Humans have limited time, limited resources, limited energy. We cannot choose and deal with everything. To deal with something is to sink time and resources that could have went to acting other way, the GOOD thing is to choose the best thing to do with such resources (GOD, The Way). And to “help” everyone, always, unconditionally (according to THEIR will) is to serve man and not GOD, leaves useless openings to ungrateful manipulations (and in fact harm towards others; the opposite of the goal), and is indeed something immensely selfish usually. It is also insulting to the very related concepts of humanism and the human soul; it denies others any concept of free will to help themselves; insulting to always help everyone with unimportant trifles, the important ones are the grave problems, and it is visible which ones these are. Ironically, these are also the most taxing and perhaps unpleasant (from a utilitarian perspective) to deal with, and opens far more avenues to the abyss. People generally (vast majority) avoid dealing with these grave problems, and those widely considered good are the ones that deal with meaningless trifles and make smart/humble publicity out of it. Their “soft” persona is very pleasant and lacks those rough edges; it is unnatural and a convenient lie. Socially great, morally questionable perhaps? Strangely enough this is similar to psychopathy, which is popularly considered the antithesis of this “gentle, humble, good man” archetype that people swoon over
Related: humility is manipulation. Humble people are scarier than arrogant ones.

Psychology - archetypes matter, very much, in the eyes of people. Social interactions which (without waving it in the face, of course) link to these archetypes are immensely powerful. Archetypes entail almost ubiquitous characteristics and stories, patterns in romanticism. This has potential to be an extremely powerful idea. Links strongly to the “charismatic” persona in AOS

Psychology, morality - normal people are not much better than psychopaths? Psychopath said to be awful due to lack of “empathy”. Normal people are worse, suffer from very conditional empathy which contradicts itself and works for convenience. Do they even have much empathy? There is definitely some “real” empathetic reaction sometimes; but usually it is faked spectacularly (to fit in/show their morality/impress others/not be seen as evil and uncaring, both to the other members of group and especially the recipient themselves; a very social mechanism and strategy), only to dissipate completely when the recipient leaves the room. Extreme blindness and hypocrisy due to bias against other individuals, or themselves (usually people think of themselves as great/good, give themselves infinite leeway for “mistakes” that they harshly rebuke when made by others); clear sign of lack of empathy. People are strongly socially strategic, to the point of dishonesty (even if the strategy is suboptimal, ie. shyness or invulnerability). Yet they cannot see any of this, and are blind to their own hypocrisies, lying, and lack of empathy. Like if a psychopath had no concept that they are a utilitarian strategist who dies not care about others. On top of that normal people are constantly subject to strong negative emotions, anger and hatred and (perhaps irrational and vile) vindictiveness and violence; and do absolutely nothing TRULY good. This is most people.
The psychopath is fearsome for his intelligence, and lack of charm, like a ghost. The normal person is fearsome for his inability to be consistent, the possibility of flaring his immense hatred which will manifest itself everywhere, mercilessly, against the subject, and the unpredictability of such spirals
Always be on the lookout for such hidden emotions in normal people.

 Math, statistics  - game theory, finite sample, lots of plays, lack of time/weaknesses (mental as well)/irrationalities, “average” case good enough to exploit for profitability.

Psychology - Sadhguru has “charismatic figure”. Eloquent, flowing, slow speech, making audience hang on by a string patiently using tension and pauses; long winded sentences sound so profound for extremely simple ideas (interestingly, the opposite of “straight to the point”, far more romantic which is good for seductive purposes); does not agree or concede when others ask or try to clarify something, which frames the power dynamic (HE is the wise guru, uncountably greater in wisdom and knowledge than some common man), even when dudes say the correct interpretation, he does not ever indicate any concession, always framing himself as greater, but never confrontationally, more from a wise sage persona
Robert Greene is similarly charismatic/gives off an aura of wisdom but from a separate angle. Speaks slowly, very controlled but with wide eyes and a passion; but dies not come from an angle of superiority, but rather of humility; concedes very often, shows constant agreement, frame of allyship and that the conversational partner is intelligent and correct. Ties in partner’s contributions to what he was talking about, without being confrontational or telling them they are incorrect, always finding some angle by which they are both correct and in agreement with him. A very good frame for a friendly interaction. Never any hint of animosity or unpleasant feeling, but rather of enthusiasm and openness
Sadhguru is reflective of a good “charismatic leader” style. Robert is good for “egalitarian” or “inferior social status” expectations (like with a boss, visibly more accomplished person, expert).

Philosophy - good and bad as an ebb and flow (narratives only make sense under such condition). Universe operates according to laws of equilibrium and conservation. Lower at level of this is nothingness, void. Thank God it operates on a higher dimension of movement. Equilibrium with movement involves ebb and flow, nothing is ever infinite or infinitely powerful in the domain of the universe. This concept of movement, comprising ebb and flow for equilibrium, is apparent in all great art, as reflections of the beautiful universe
Related: equilibrium -> nothing infinitely small?

Music, mathematics - Bach as similar to circle in terms of the plentiful continuities in his music. A circle always remains continuous no matter which point you view it from; and there are an infinite number of such points which are different in the global view of the circle, but locally amount to a “valid continuity” nonetheless. (Explore circular shapes as the only such shapes, which are connected, yet continuous; lines/functions as non-connected). Bach’s music can be heard/“viewed” from an huge amount of different perspectives or lenses and still remains an amazing song, all of their perspectives result in validity as much as the next. Then, in the global scheme, perhaps can also be viewed as a circle; unlike Beethoven or Mozart etc where there is clear foreground and background, it is not a valid lens to treat some aspects of the foreground when they are background; whereas Bach so many (possibly every) perspective is a foreground. Like the global view of the circle; the grand scheme of al perspectives of Bach’s music is itself a valid perspective.

Philosophy, lifestyle - Aurelius, limited time, inspiration as divine, must go with that flow

Aesthetics, philosophy, music - Kant’s view of music as “lowest art” due to lack of representationality/culture (debatable in later times; Beethoven and romanticism as clear link to heroic story, clearly cultural; impressionists as clear non-abstraction of natural imagery’s impression on humanity). Kant’s point mostly applies to earlier music (Hildegard, Joaquin, Bach, Mozart). I disagree with him for his very reason. The beauty of the universe is most purely distilled in music, without attachment to any cultural societal ideas of such; music os more pure of a reflection. Immensely beautiful

Music - Schubert D960 - beautiful, resolution, resolved acceptance of death. Comparison to Beethoven — idea of overcoming. Schubert as more personal, Beethoven as more universal concept; personal suffering (death and its acceptance) vs. Grand scheme suffering in life (choosing the beauty of life in face of evil and pain)
Mvmt 1 middle section as initial “tears despite trying to smile” (then a calming down, resolution, acceptance). Empty space. Interplay between “moderated” motif    and bass clef trill. Both depressing and uplifting. Death, unfulfillment that will never be resolved; but acceptance of such, looking back on life and an appreciation of the beauty that has been seen in his time. Surges of energy (crescendo in the melodic motif), to move forward in spite of the ever closer void, heroic. “Molto moderato”, a touch of absurdity, connecting to the subject matter. Final resolution section as connection to this idea, grey and light at once, making the whole thing a clear area but interpreted brightly as possible (a very clear, visible grey uncertainty, followed by lightness; that causality shows a light interpretation of something clearly do grey, uncertain, absurd, with clear potential resolution into darkness). Final, repeated chord (with important pause) shows a strong resolve to the positive lens
Mvmt 2 as shifting from sadness, defeatism, to smiling despite the tears (key change). Initial progression: very dark, gloomy, shift into section of relative lightness (with the minor undertones), clear knowledge and affect of death, then the remembering and reminiscing of the good parts of the hero’s life. Then back to gloominess, a knowledge that he will not return to those moments, they will be lost forever, they were meaningless, all of them that could have been executed upon are lost. Like a gloomy resolution and “acceptance” with negative lens, to be defeated, resigned. But then an uptempo buildup, of hope? We can dance in spite of everything! We can always dance! The seriousness hits again in this uptempo section, but resolves into positive acceptance! The gravity of the situation is presented again, like a temptation to lead us astray but the hero is resolute, overcomes this darkness and resolves back to the light. He begins the journey, reminisces again about those good times he know he will lose forever and can no longer resolve, and the final section leaves us on a cliffhanger…. What did the hero decide? Back to the main section, a recapitulation of the initial idea, like a time warp, but now the hero has changed his mind, is a different man. Presented by the devil with the same grey and grim situation. Then: the light is immense! The hero has decided to move forward with a smile, even in the midst of the grim undertone. Ends on a graver note, but still light. Like the hero is out of his fantasy, the thrill of his decision, and reflects seriously on the state of things, but remains resolved, accepting.
Scherzo is like a dramatization of these concepts, the projecting of them into a dance on a stage. A meta-interlude. Something prepared for the audience as they reflect and internalize on what they saw, eating their popcorn. Like a detached perspective/summary on the protagonist. Very interesting.
Last movement also from a mix of perspectives, upbeat initial theme, detached, like spectators of a carnival, theme gradually becomes more personal, emotionally significant, as if sinking further and further into the individual’s consciousness, an agent with free will, rather than a mere object in some show. Jarring juxtaposing shift into strong dark chords - there becomes an awareness of all the darkness in the protagonist’s life, that was once invisible to the observers, who only see the satisfied state. Quickly shifts into positivity however, as the protagonist reframes his situation; it’s the same melody and rhythm but the protagonist has put a positive, hopeful twist on it. Progresses uneasily in the end, keeps suspense, what happens next? Like the end of a dramatic TV show where the character only smiles, what could that mean? Ends in an abrupt happy ending, absurd on purpose perhaps. It was happy all along!
Link to literature, narratives, perspectives. This is amazing art, could you imagine literature with such a narrative structure? Would be amazing

Psychology - better ways of personality tests, currently down through self assessment of action in given situations (biased), far more generalizeable and less easily biased is to evaluate the components of action — ideologies, motives, sensitivities, base loves/hates, ways of sociability, view of self in that regard, etc
But they see personalities as distinct, which I completely disagree with. I think people are mostly the same (extremely similar) thread, act the same way under the base concepts; personalities are more like strategies and masks that have been decided upon, with influence of confidence/strength and weakness, linking of whatever thing they’re good at due to their environment. Modulated by ideologies and beliefs in them

Morality, philosophy, aesthetic - art and morality/goodness are intrinsically linked. Motivation for morality is the same as aesthetic appreciation and value. Why be righteous? Perhaps the question amounts to: why spend time on art or adventure or friendship (as arts/values in themselves rather than means to some power-related end), that could have been spent on more work/power? The question is absurd to me and psi’s so my everyone else. I love art, this is an axiom in itself, and it does not make sense to rationally justify such value; it is there and natural, this things emanate from that and not vice versa. So it is with morality. Reduces to same as “pure mathematics” (like pascal’s pensees). In the limit, pure mathematics is an absurd, meaningless, unreal concept; pure Yang. We NEED and want aesthetic, and aesthetics are inextricably embedded in reality to begin with. So “why morality” is absurd.
Indeed psychopathy, and a love of power over all else, or math over all else, are themselves (false) aesthetic values or lenses. There is always an aesthetic/lens (the concepts are linked; the lens is an interaction between True Aesthetic and the self’s animalistic desires).  There is never true lack of aesthetic in anyone’s concept of reality. Everyone this always has some (perhaps) false guiding morals. Might as well go all in here, and aim for the highest and only true moral.

Art, mathematics - Leonardo
Putting 3D perception into 2D plane (paper) is interesting. The real world is popularly considered to have 3D, and the basis for such a lens is length, width, height. A paper is inherently missing one of those dimensions. The solution is to change the basis. “Height, width, length” is considered a “real world” basis to describe objects (real and independent from perception). Our perception merely assesses these real attributes of objects. But art is intrinsically a matter of perception rather than reality of the depicted objects. Let’s then switch the lens from the world of objects to the world of our perception of those objects: meaning, let’s examine: how do we know the height, width, and length of an object? Imagine our visual perception taken at any static slice in time. It turns out we can assess using a 3 dimensional basis: position x and y (like the length and width of a paper) and colour. Using these three dimensions we can generate any realistic image like we would perceive it with our eyes. This tends extremely well to the domain of paper. When we say 2D drawing, this implies only the use of 2 position components, but truly it is 3D, with colour; and this “basis of perception” is intimately linked to an understanding of the world of objects, and in art we can then link to objects from mere colour, x, and y.
This is linked to the idea (roughly) of neural network. Neural networks are only one specific class of the following concept but bear with me. Imagine art on paper as mapping from “raw perception”, that can be described by colour, x, and y; to a world of objects, but also more than that, the world of concepts. This can entail many more dimensions. This links to “understanding”. A bridge between the inherent gap between perception and reality. Perhaps the map can be computed as some chain of functions, like a neural network, and also the brain. If we assume the universe as having order, Yang, predictability from mere perception, perceptions as having value and bearing on the order of things (all valid assumptions), then perhaps such consciousness can be modelled as a function.

Art, lifestyle - the beauty of imagination. Can take you anywhere, and you can be the pilot. Any scene or context. Of course informed by reality, but art is not constrained by it. (Link to earlier note about photography Vs. Painting).
I am imaginative. I shouldn’t be ashamed of this, indeed it is a reflection of strong sensibility to aesthetic value; rather i shall sink into it like Leonardo, ride it into something meaningful, rather than a waste or a sink.

Religion - KJV Acts
Gave acts to the apostle “through the Holy Ghost”. Holy Ghost as the direct conduit to the right thing, short circuiting the inherent problem of the gap between knowledge/belief and truth. It is inherently “felt” rather than rigorously proven. It is movement generated by the will of God, along the righteous path. Listen to your soul.
1:5 - “Ye shall be baptized with Holy Water…” there are links between Jesus providing water, and baptism now being done with the Holy Spirit, rather than mere immersion in water (link to movement from “logical rules” to the immense feeling and motivation, water is a physical, object, rule based concept, the ideal of which isn’t really felt by those participating in of administering the ceremony, but the Holy Spirit provides a Christian with all the motivation and joy in the world to follow the Way). I feel the Holy Spirit. Can I consider myself as “chosen”? In either case I must follow the Spirit, I have been turning away from it so often. Listen to it, pray, reframe and fight temptations; this is the way.
Acts 2 - the Lord gives the 12 the power of speech in other tongues. Some still deny the divine influence, and explain it away by suggesting they are merely drunk, mocking them. This always has been, clearly still is, and always will be, a theme. Common folk trying hard to deny God, or concept of Christianity as true, even when such influence is clearly there, and the miracle they claim to seek is right in front of their eyes; in fact they double down on villainy. Peter sums it up well:  “for these are not drunk as Ye suppose, seeing it is but the third hour of the day” (Acts 2:15) points out that it is obvious, yet the denial is still there

Philosophy, lifestyle - Meditations
Direct everything towards a single principle; resilient to all distraction, and framing every other thing, and providing value to all things; yet still “something” in itself
Incredibly important - he is talking about not needing to fear leaving the world of men and evil, and turning towards the world of God (interestingly and perhaps ironically parallels Christianity), then says “if they do not exist, or are not concerned about human affairs, what is it to me to live on a universe devoid of God or Providence?” This is incredibly interesting, but perhaps incomplete. Indeed if the universe and any given life is meaningless in the grand scheme of things, this might even push one further towards the world of pleasure, as pleasure becomes the only clear Higher Value, and life becomes lived, though meaninglessly, with random pleasure in mind. But then again, such a view is naïve. If people were to believe in a lack of God or Providence, and accordingly align themselves to their own interest without shame, then we must consider that the “religious life”, the profound and meaningful and virtuous ways of life, remains far more rewarding than what any short term pleasure may offer; and this is proven by the way people have been living their lives, no matter what there is out there, this is clearly a much better way in terms of personal satisfaction. Thus we get to the same conclusion; living as if there were Providence is not merely an optimizer of expected value under the uncertainty of the existence of such Providence; it is the best way of life in either case.

Education, university not smarter, high school only ppl don’t study or have such mentality, unexpressed intelligence vs clear crystallization of academic ability on those who study over much longer periods of time with more conducive environment (meta learning), strong gap between academic folk and researchers in many ways, IQ is a moot point for these reasons and it sang even define well what it’s trying to measure, intellect as dynamic and not static, job role as more preparedness through repetition for IQ test (unfair advantage), tests prepared and circlejerked by folk who don’t have high enough IQ to understand intelligence to begin with let along measure it by proxy, scoring system incredibly unsatisfactory and too sensitive to insignificant mistakes, time of completion; not sensitive enough to more creatively difficult problems that would actually tease out high IQ, and is bearing is completely renders futile when we consider confidence vs self doubt, stress, mental state as inextricable factors that bubble up in high pressure, high personal importance, timed tests. Different classes of intelligence (though less than suggested by IQ), high IQ more accurately predictive of high intelligence than middle, though with lots of obvious false negatives (Shakespeare, Beethoven)

Look into Malcolm X’s communication/debate style

Music, psychology, neuroscience - imagine musical progression as reflecting human voice. Human voice subtext is interpreted in terms of relation of the vocal progression to an established baseline (established early on) as well as our own expectations

When walking, eyes naturally veer down to the right when unfocused; move to the left instead, introduces resistance to be overcome, and puts us into a transcendent state

Lifestyle - strength and calmness and focus amid chaos and disorder and violence or threat and anxiety

Psychology - Greene AOS -  Greene is amazing but clearly not even he is free from his anathema irrationality, claiming Joan could have sensed the king’s trick and easily picked his pampered face from the crowd. One could only attribute such thinking to absolute genius, which is slightly unconvincing, but clearly this is a staunch agnostic/atheist. Pretty much the only plausible explanation under such a lens. Needs to then prove to us and justify himself that she made mistakes etc and is “indeed human”, as if needing to prove lack of divine intervention.
“Anything that hints at the otherworldly or supernatural powers will create charisma”… interesting statement. Obviously has to be played right. Especially from my “lowly” position. Cannot be arrogant, must be humble, due to lack of anyone to vouch; otherwise people will league to prove me a fraud or deluded narcissist. Act carefully and strategically; though thankfully, don’t have to completely hide our powers. From my end, I have intellect, willpower, courage/bravery and ability to remain immensely self assured and focused in tense situations, true goodness and many incredible manifestations of that, and very high lofty ambitions that shall be realized. As if divinely chosen (and I do see this in myself), to reveal and uncover the beauty and fabric of the world, and to use my strength to do good things when they are difficult, that can have immense impact (think about this)
Rasputin - links to archetypes: the “strong male hero” full of grace and confidence and love but with an emotional side (which is still attractive in itself, “justified anger”, meaning will take action for what is right and is stirred as such, with no doubts of him  being prone to “switching sides” by some tempting circumstance like someone emotionless would seem to be, as emotion is convincing, and as such irrationality is embedded in its own evolutionary strategy funnily enough, as these social perceptions of emotionality vs. Aloofness rely on irrational attachment that is perhaps beneficial to the assurance of others). This “weakness” is attractive because it shows a link to the other social actors, that they can seduce him, out of this principle, that he is not universally fair and equally judging/loving of everyone, thus they have preferences and they can be the ones to live up to such valorous ideals. People love emotionally binding over things, and this is perceived as an open door; pure grace and zen is boring to others, versus that emotional alignment over something deemed meaningful. The jarring switch is itself something the brain is attuned to and very attentive of, making him someone people are interested in and want more of. The juxtaposition is mysterious, he eludes explanation, to be fully explainable is fodder for people moving on.
People who appear great or impactful of immensely graceful and good on a deep level probably have a very dark side and character; people generally (and naturally/animalistically/honestly) would not act like this, in a way that has such hypnotic sway over people; this can only be consciously practiced and cultivated, and thus clearly has subtext of desire for power, control, ego gratification, being on top, all the things that come with it. Good with such sway is generally a contradiction. Watch out for this, but play along of course



Project: think about good thing, and ambition, that could be huge
General - get a lot of money, and break out of corporate structure after I get enough (a general desire, of freedom from annoying power over us, a forward and free thinker, adventure; makes others daydream), then do good thing after good thing with it: he’ll sick, poor, homeless (individual), money for hospitals, schools, water plants (societal infrastructure), environmental and historical efforts (my love of the world); loop on stuff that’s generally bandwagoned by my (“higher” but not highest) striatum of society (to do) as well as the individual I’m speaking to. “Serve as inspiration to other kids like me who are misunderstood, who’ve been robbed of passion or love etc, don’t think they’re enough etc”, there comes a point I cannot so things to help the deep problems of an individual, nor do I want to, because they have autonomy, they are their own masters, not me, have their own uniqueness, and I want to reach as many people with difficult lives as possible; greatest thing I can do is to show myself as an example, not necessarily to be emulated, but as a blueprint, and signal of hope. Need to link this to romanticizations of “high level problems and insecurities” faced by everyone else, like insecurity about not being good enough (in one’s own eyes or those of others), of demotivating and confusions about passion or path or one’s own life, of the viciousness and unexplained violence of others that leaves a mark, etc etc. I’ve always cared so much about individuals, and realize the best thing to d here is to remove myself, but in reality, there is an effort, a meaningful and good one. Care about societal aspects and infrastructure etc only to the end of enabling individual actualization. Many oppressed societies with lack of adequate and essential infrastructure or other needs have such an immensely rich culture with so many valuable ideals across the board, different cultures like pieces of a beautiful puzzle

Project: start engineering and building small things. Like circuits, hardware, robots.

Philosophy - to get to a deeper understanding, beyond the popular books and inevitable sway of their fallible writers, and further into the realm of the truth than of social absorption and “learning” from the teacher, and learn from nature instead; one must think from first principles, and write the book himself, though perhaps using previous books as a head start, or clues as to paths trodden already

Philosophy - Confucius analects
2.3 - policies and punishments versus virtue and happiness and the way. One is skirted and only shallowly believed in and subject to be scaffolding for the carnal and misaligned desires underneath; the other is self fulfilling. Link to Christ as the Way vs the law of Moses
2.4 “Learning” (and discipline) as good basis for following one’s heart, gets you to a state where that can be possible and consistent and meaningful and aligned with what is truly right
Funnily enough Confucius says so much about being filial and always obeying parents, perhaps this thought is embedded in much of Eastern society now, but ironically as policies and punishment rather than actual personal alignment… and you can see the dissatisfaction growing among the youth, having to obey when there is conflict, they verbally disagree with their parents and often harbour blame or resentment. I personally disagree with this notion of compete filiality; parents are themselves imperfect and often selfish, and do not understand their children’s own alignments; their own takes precedent. Traced over generations this is immensely limiting and people end up converging away from any individuality and towards a static view of things without diversity that could only be provided by a personal touch that has been driven out of them by submission to elders and parents. Imagine if Mozart listened to his father. Parents can and do drive people away from the “li” that Confucius preaches so in the end the point usually ends up counter to the philosophy. I understand that many of these philosophers are concerned with limiting the chaos inherently associated with unbounded desire, and do so by trying to find some “strict” strategy that is perhaps stricter than necessary but will lead to the desired outcome anyway, like a lower bound though not a tight one. But in the end perhaps a lot of these entail their own side effects.
Concept of filiality clearly resolved the issue of people who clearly don’t know better, aren’t wise enough, etc; assuming that parents have already been taught the way and stray to it unflinchingly which is pretty much not ever the case, but in theory it does resolve this problem of naivety, which is clearly present always in all society. But it also prevents any further Conficiuses (Confucii?) from springing about. Perhaps “good for the norm” though, perhaps in the frame of society, people don’t need a better way than the one already provided, which is “good enough”, and innovation is not needed per se. But then we must understand that there exist other societies and other actors, who are not aligned to this way of li, and rather go against it and desire conquest, power, disharmony, a lot of things that at some level go against this philosophy which is good intra society but suiboptimal competitively when up against an invading force that has used its rebelliousness and unobedience and discontent and desires for glory and selfishness to innovate strategies and tools of war that can decimate those who were peaceful, harmonious, and obedient; and when they do, the desired way of life of Li becomes clearly infeasible and barred from prosperity by the barbarians who hold them into submission and allow evil to fester.
Confucius is clearly concerned with intention over action, which I completely agree with. 2.8: it is the expression on the face
2.10 - observation of someone’s motivations, means, desires/alignments. Where can he hide? The closest we can get to the soul of a person is an examination of these things. Not words alone. Words only matter (aesthetically) insomuch as they reflect wisdom, and how they tie in to those other things
2.12 - “the junzi (morally adroit person) is not a vessel” — liner notes state that the meaning of this emanates from vessel as implying limited capacity and only used for certain things. This goes to show why one should not blindly trust so-called experts. They are not prophets or even geniuses (usually). Though perhaps Confucius would get mad at me for taking this viewpoint as I am not obeying my elders…. Why fake vessel as “limited capacity and use”, instead of the more intuitive “something to be used as a conduit by someone else, a means to an end, with no will of its own; to be used as a method of mere transport and diffusion for someone else”? Makes more sense to link to blind principle following (vessel) versus alignment to li. This is validated by the immediately following 2.13 where Confucius explains a junsi is someone who tries something out before following it. This gives credence to what I said, they don’t merely “transport” things without any aesthetic alignment with it.
2.15 is incredibly interesting — study but don’t reflect (vessel) you’ll get lost. Clearly. A shallow understanding cannot be generalized across the map. But then: the man who reflects without studying will get into trouble. Interesting, this becomes a problem of misalignment, perhaps implying people, without discipline and instruction, default to selfishness; and those who reflect with such a lens tend to break the law, cause chaos , lead to problems and society in the wake of their selfishness; basically like psychopaths. Or on the other hand, implies reflection based on some faulty Allen’s or set of immediate axioms. Causes trouble both in reality checks, and in negativity/mental state/paranoia, etc
2.16 continues - those who go to work on a different strand cause damage. Liner notes are once again pathetic here, implying that this passage is vague and reflects the value of teamwork, which is obviously missing the point and only a shallow understanding of metaphor. He means, in terms of society; people who are unaligned will clearly act for means independent or against the collective, when given the chance.
Link between obedience of parents and Christ saying to obey the human law where it does not conflict with the way. Clearly optimal.
Next section, duke asks how to get populace to obey. Confucius says to lift up the great men above the evil ones and vice versa. He hits upon an incredible political strategy here. This links to the concept of societal alignment. To get people to obey they need to be unified and aligned on some front, and children have this ingrained in them on the form of justice and “the right thing to do” and respect for elders etc. whether they end up acting righteously in the end is a different story, but the point is, their concept of justice is defined as such, and this is their basis of alignment; when corruption is evident, or those very acts of righteousness that were taught to them are punished or rended to pain, whether abetted by the government or not dealt with, this is an evidence of misalignment; and the root of obedience is alignment. Misalignment leads to disobedience. Examples of present day government using this strategically, by playing into popular opinions of who is right of wrong, and riding that trend to choose who to uplift and who to biology, creating “simulated alignment”. Though in societies with considerable members and power on opposing sides (the United States), this clearly increases alignment from one faction, while multiplying animosity on the other. We are taught justice is the highest of values. Hatred of admiration of others involves perceptions of their righteousness. Slander involves demonstrating a person’s glaring villainy or rejection of moral standards. The other important dimension to be satisfied is perception of skill. But obedience happens through justice
Though it should be noted that Confucius is speaking in strictly moral terms here. And at the same time it ends up being a great political strategy. Goes to show the two do not have to be disjoint. There are many possible viable strategies for the sake of the end/value of “power” that are against the value of goodness. But if one is truly aligned to that strategy of everyday goodness then it hits both. Goes to show the same morality applied to oneself and smaller interactions and groups also is meaningful for the higher levels of government; it is universal. Though perhaps when integrating the value of goodness into things, the upper bound for other “values” decreases than if they are psychopathically pursued in a vacuum without any lens of goodness. We must be careful before saying this applies to power. Power is a broad term and involves more than mere political presence; perhaps it can be argued that goodness increases the pure virtue of power in general. But if we take the set of values that form the basis of psychopathic ladder climbing, and treat the end goal of this system as a value in itself, then under the lens of goodness we are limited in how much we can pursue this; but also perhaps, goodness could take us to an isomorphic “end” that the psychopath aims for, detached from its value system (the means), more meaningfully and efficiently than that other value system could; while providing further a far deeper and richer set of values and experiences: it overwhelms these other value systems. See “living righteously” as best way to live. Living righteously takes one out of the box; it prunes useless, waste of time ends, and changes the system to one that is far greater.

Music - in Mozart, Bach (Brandenburg Concertos), there are satisfying moments when the orchestra’s lower/higher components trade lines, like a conversation, a discussion, eventually converging into togetherness and unison, both voices playing together on concert. Like mid and body, and their eventual alignment, in “passionate movement”
Mozart piano concerto - piano is a singular yet immensely important voice. Piano and orchestra trade off lines and emphasis, and feed off each other. Similar to a leader and the tribe. The leader makes a speech, and the crowd enthusiastically chants the slogans afterwards, emphatically validating the leader. Leader and tribe gong through turmoil together in turn, like mind/thought and then body/action, or like a chain of command; the center/general, and the peripheral/soldiers, fighting off the chaos together, one cannot work without the other; piano weaves through all the different orchestral timbres, gracefully managing all of them as they feedback into it. Piano is immensely graceful and natural in its progression. Leaders should strive to emulate this for purposes of their charisma and hypnotizing of the audience. Lines that involve a tease/hint of uncertainty, but then an immensely satisfying resolution, a “return home” to the tonic, a conclusion of triumph. “We will win”, optimism.

Philosophy - rationale for innovation - most philosophers would agree to act according to the natural or divine order of things, and embrace the beauty of that; this divine order has an aesthetic value to it. Then it would make sense to seek that beauty, to embrace, appreciate, and act according  that natural beauty as much as we can; to explore it. No one would claim to have completely uncovered the divine, or the entire beauty of things. If this divine order had aesthetic value, which it does, then to love nature is also to explore it and think about it, as Leonardo and Einstein have done; this is innovation, this is science, this is thinking outside the establishment. Though of course when glory is the end goal, the point is moot; but in terms of love of the universe, being completely zen is not consistent there.

Religion - saw some clip of Mohammed Hijab vs Peterson, Hijab claiming there cannot be 3 all powerful beings, that Jesus being limited is an affront to logic. Jordan cannot answer well, sadly. The explanation is that the Trinity is a Catholic concept and not a Christian one. Trinity is an attempt at a “logical deduction” using Bible as an axiom, and the result is used as a fundamental belief in that doctrine; I am not a Catholic I am a Christian, if you want evidence to doubt the Catholic Church, see that their doctrine says they are always right, then a millennium later they admit they were wrong about some judgement or action. Clear contradiction. In Bible, there is a separation between GOD the FATHER and the Son, Jesus Christ, “The Way”, the absolutely optimal model of humanity, the embedding of the Father in the World, and the Holy Spirit as the absolutely optimal voice to listen to to guide a person there. They are not of the same class. Not three “beings on equal footing with the same background concept” like these folk are erroneously arguing.

Philosophy: watched a snippet of Zizek versus Peterson, Zizek says you shouldn’t set your house in order but also set society in order cause society influences your own house, Peterson can’t really answer too satisfactorily except to say “maybe in setting your own house you can get an idea of how to fix society”. I agree with Peterson’s claim in the end (“start with yourself”) but not his explanation, in fact here it is very unsatisfactory, most people simply are not smart or aware or caring or strong enough to set society in order at all, even if they “start with themselves”, and will not be able to generalize their own “fixing” to that of an entire society. A lot of societal change is effectuated not by everyone fixing themselves, but simply being roused to rebellion. But Zizek is wrong too, claiming that peoples’ disorder is caused by their external environment (society) rather than internal. All the ancient philosophers woold like a word with you, and so do I. It is clear even when people have everything they are prone to discontent, and are not even moved in themselves, and will not put on the effort to benefit society selflessly; clearly external forces have less weight than is obvious. When disordered people band together and try to change society, without having any order in themselves; odds are they won’t change it in any sort of ideal direction anyway, and will make things worse for themselves and others. Obviously no one will ever have everything (if anything) figured out; but clearly there is a point when someone is more “ready” and strong enough to take on this responsibility (this is a point Peterson seems to make a lot in general, it’s strange he didn’t think to link it here). Putting the room in order at least provides that required strength, and other things come with it like the open mind, and self awareness to understand and feel if one actually wants to change society at all in this way. Realistically only a few people need to put their room in order; the “leaders” and intellectuals; other people generally follow them and their rousing speeches; they are the only ones who need their room in order. I don’t think just anyone can or should become a leader, and I don’t think just anyone can and should become an intellectual/wise man/philosopher. But at the very least it is better for people to be in order than without. Or is it? Think from the perspective of people at the top, who value the summit, perhaps it is better for them to stay in disorder; but to feed them a false story, and spring in them false beliefs of what order and chaos even are, and as to the constitution of what it means to set your house in order and fight evil and do the right thing, and to think outside the box, and as to the state they are currently in, and as to what the better state really is. Perfect; then people will take all those beliefs and inclinations to do the right thing, and to effectuate action and power, and to help society; but to direct them towards nothingness, so they feel they have done something great, but have done nothing at all. The rebellions they need to organize,  and holy wars they need to wage, and righteousness and virtue they need to demonstrate, and heroism they need to realize; all towards something irrelevant, but closes the loop of their archetypal embedded narratives, and motivations.

Psychology - imagine being absolutely powerful; to the point of having no uncertainty in the outcome of conflict, powerful enough to always be assured of one’s own victory. What an immensely boring life this would be. It is better to be less powerful than this, a power vacuum is always needed in the life of any individual, for the sake of any excitement or novelty or meaning at all. In the high ranks, people are happiest when they have enemies, and suspicions. The rich elderly folks look back most fondly on the times they trounced their powerful enemies, and outcompeted their peers, and did all those things people told them they couldn’t do, and sniffed out the sneaky traitors; all meaningful because of the concept of overcoming huge challenge, with an uncertain result, that was overcome by the sheer capability and superiority of the person (such is their interpretation). Humans tend to need such narratives, and events that fit into them; if none are readily available they twist existing, initially lame situations, contexts, memories to involve these things; mundane events take on a sinister meaning, and the actor gets his successful revenge and trounced the “disrespectful”, “uncaring”, “annoying”, “disloyal” enemy he has created.
The Machiavellian and psychopath aren’t super satisfied when they are on the throne, but are happiest at the point where his careful planning plays out on one distinct event, the surprise and defeat and anger on the enemy’s face, and the ecstasy of the smirk on his own. They don’t live for success, or the state where they have the utility; but for the moment when they won.
Perhaps man is in fact at his peak then when the external state is repeatedly disordered, that he may set it into some order over and over again.

Philosophy, logic - people intrinsically do not understand what it means to truly help or do good for someone, but let’s keep it vague. If someone is beyond help, nothing you do will help them. If someone is not beyond help, they do not NEED any material object you can donate to them, and such donations are thus not directed towards what is deeply helpful. The idea of donation in itself is also slightly insulting, and removed the notion of power or will of the recipient. The best thing you can do for anyone is to find a way to make them aware of a limitless well of will and internal strength and its potential for change and power. Good towards a person should be done from the lens and interest of their own power and free will, and not from the lens of donation, which is either self serving in the end, or naive and endlessly manipulable; either way materially eroding, and not MEANINGFULLY helpful in the sense  aligned with the good that generated such action to begin with

Math, philosophy - math popularly considered “inapplicable” and abstract compared to the more practical stuff like economics or psych. This is a falsehood; there truly is a mapping between mathematics and the world, exactly because of science; if we believe in any bearing of science, then we believe that math can be meaningfully mapped onto the world. Math is merely the language of deduction and rationality according to some  system. Math is obviously the most “real world applicable” discipline of all. Fused with creativity, this can then be broadly defined as “science”, and the marriage of these can provide a rational basis for absolutely everything else, including economics and psychology and even religion. People say abstract math is meaningless, but it obviously is not; and explores truly fundamental aspects of the world of logic and the fabric of reality which is already shallowly entangled into other disciplines where it has found application. Knowledge of math furthers our understanding and even explorations of the universe itself. Think of pi and the circle. People currently just haven’t mapped a bunch of stuff yet

Religion - Christianity: we must act out the right thing according to our context. Cannot judge others, or other religious faiths, perhaps they follow the way, in the way that the Spirit guides them, but I would have to confirm this. See Nebuchadnezzar and Cyrus in Old Testament. Time is one such context clearly, see Old Testament versus New. God is the Lord. We follow what WE feel.
The Way is about action. People are always wrong. Yet still have strong faith, and are righteous. Incorrect or incomplete conceptualizations (belief in Catholic trinity etc) are independent from the Way and righteous actions.

Religion - question of free will: it is logically an illusion once we get into the weeds. God is omnipotent and clearly knows how we will act. Thus our free will is only our conceptualization and consciousness of ourselves in the world. So we must ask ourselves if it is pointless to be living, if God already knows what will happen. Obviously this is unknowable. But I only am conscious of myself. I do not have consciousness is another person. All I can know is my own. I feel as though I am touched by the Spirit. And all these things like pain, suffering, struggles, learning; make righteousness have meaning. I see ecstasy, that life, and its reflections of the divine, are more and more beautiful; and I am immensely satisfied, and this shall continue to grow; I see the Way as immensely beautiful. God loves His own. There is a clear concept of aesthetic value. Even if there is no Fred will; the unfolding of my story is immensely beautiful and meaningful to me, and is evidence of God showing his infinite love. As for evil people; that is unknowable by me, at all, cause I am only conscious of myself.

Philosophy - Confucius 2.20 - idea that demonstrating goodness and virtue has a strong and meaningful impression on others to the point of persuasion

Psychology - people want to be subjugated. For most its to a leader, a cause, a dominant individual, a “respected” partner, “growing together” with a loved one involves an ideal of subjugation. Even for those at the highest striatum (very rare), there are two broad types: Alexander the Great and Stalin. Alexander saw himself as a vessel of virtue; subjugated to the Gods; he had no perception of himself as being above the divine but rather a force chosen and inspired by it. Perhaps Stalin saw himself as subjugated to no one, but he was a vile and brutal psychopath; which is a far worse deal. In fact, for someone with absolutely no desire or concept of subjugation, it is hard to see any other development than that of a monster and a psychopath, trouncing along on a meaningless and endlessly dissatisfying existence. Perhaps psychopathy is intimately tied to a lack of concept of willfully subjugating oneself or being subjugated

Project - chatGPT is merely some conversational agent, powerful but not that powerful… what do people want?
Our idea can cater as “personalized AI” that generates content based on its knowledge of the user
AI for some “social” end: think about
AI to link people together or connect people?
Or stuff like this, using data mining of AI’s judgement of a person

Physics - what generates human movement?
The physical world is understood through cause and effect, of objects through time contained within the universe, and channeled through basic forces.
In the human, thoughts and movement would occur through the development over time of an “internal system”, that can be likened to a differential equation, a process, running through time, affecting both itself at the next time step, and also the “external” human body, through neural connections to muscle tissue, etc. The state is also affected by external forces in the world, through the senses; vision will make the photoreceptors in the retina vibrate; touch will pinch the nerves of the skin, etc; all of which get further processed downstream in the system, which sends signals accordingly; electrical force gets translated into kinetic energy in the muscle tissue. Like a neural network acting on its own in the world. Almost like a mathematical object. Consciousness and “unconscious processing” likewise can be viewed as linked systems, and can be simply described in a system, in the same way that neural network architectures encode assumptions on the way to solve a problem.
Perhaps this can be important for our AI system. Pretty close to RNN to some extent

Philosophy - Nietzche Gay Science
Very interesting idea: people tend to be concerned with preservation of the human race as their chief project, even if they have no care in the world for others; arising from the obvious evolutionary drive. Think about it: even when people are stepping over each other to climb the ladder, the ones at the top have objectives that in a way “benefit” society, or innovate for it, or lead it; even if they themselves are detached from any true love or alignment towards the humanity they are helping
Wow… he has very similar thoughts as me on the evolutionary strategic benefits of these negative emotions and actions and people
Side note: this is harsh, but depressive loops also have their evolutionary role; they keep the depressed person in that state, which others hate and are annoyed by, furthering their exclusion and lack of contribution to anything; it is evolution’s way of pushing aside the “weak”, who only got in this more cause they messed up many times or are too soft, etc.
“Squandering, vanity, etc seem like suboptimal strategies but have actually led to the preservation of our race”. I would be careful here. I see what he is saying, but it is more that it allowed for certain races to “dominate”, and equivalently to not be dominated by those other dominant ones (there is a clear link between such vanity and conquest and innovation). But it is hard to apply this when considering the global scale of the entire human race. Of course, we still exist because of our invention of tools, creativity, loyalty, love for one another (working in groups). In the hunter gatherer eras, vanity was at play to some extent, but it is hard to see it as the main driver of things rather than these more heroic ideals such as passionate creativity, group bonding, emotional meaning. These things may have existed then in more of a vacuum free from vanity as the original spark from them; back them existence was more “simple” (in terms of mathematical complexity) and more natural; but since the dawn of agriculture, the decline of nomadism, and all the things that came with it, there was an immense shift in our being; and vanity definitely takes a driver seat now;  but in the grand scheme of things, perhaps it was never really necessary, and creativity and emotional links were powerful enough motivators and values in themselves without ulterior vanity.
“What may have harmed the species is now gone”…. Interesting. Even if one of these historically devastating things did arise, it is generally, in the grand scheme of things, a cakewalk to ensure the survival of our species, as the essentials (as far as we can see) have already been innovated, and we have plenty of historical precedents to emulate and textbooks to read that have already been written. In other words, society can function on autopilot (unconscious), and be completely fine, just by blindly following its current configuration and standards.

Neuroscience, lifestyle, philosophy - often I am tired after engaging in some task, I do not notice (and this links to the point I’m about to make) but it seems that music plays in the background of my head. This is a clear sign of the unconscious mind taking over, of the locus of control being stripped away from the conscious and to the direction of the unconscious. The unconscious is mere patterns, determinism, old habits. As long as the unconscious takes over there is no growth or direction or orchestration or “movement”. To wrestle back locus of control is to direct your life, to learn, to earn. To let the unconscious do its thing over and over again is to use your free will to choose to not have free will. But then are you conscious that your unconscious is taking over, when it does? Well now I know. Now I have that awareness. So the point is moot. I always feel it either way.

Music - try it for meditation purposes, and it definitely serves a role there, with eyes closed, focused. Lay off it otherwise. It is far more freeing and powerful, logically and from experience, to act and deal with things with a clear mind free from music

Music, neuroscience - related to above: I find that headphone usage in fact tends to “dull” my brain and mental state. Either long exposure to loud music, or Bluetooth waves, or pressure on my head, is causing this, either way keep note of this, and limit usage to short intervals

Lifestyle, log - today I was in the cold shower all the way cold, and for a long time, gradually decreasing the temperature. Bravery, excitement, focus on breath, routine (chest, head, back while shadow boxing; intense focus throughout). Strong ecstatic, exciting, and energetic effect

Lifestyle, philosophy; religion - related to above. The will, and by extension the right thing, is always applicable. It is applicable not only to dealing with action, or to dealing with an emotional state (calm), but also dealing with fear, treating emotional state as an external factor, like acting even under fear or pain or lethargy; this flexibility to conditionality allows for its unconditionally; it is applicable and the same at all levels. All that is required is consciousness of the areas in which it may be applied, both in the thick of these situations, and in the grand scheme of our overall understanding of reality and “conscious value system”, and also the knowledge that we have an unconscious value system, and perception of its manifestations.

Philosophy - Nietzche talking about species focus vs individual, claiming most focus on species without knowing it (disagree, slightly absurd, see tragedians; evolution does not work that way, individual love factors in a lot; heroism IS evolutionarily meaningful and important and naturally revered); will probably say that one should be aware of this comedy and unconscious process and REALLY focus on themselves, this is true individual freedom (to continue)

Adherence to Nietzche has led and leads to both people and society getting more and more lost, these things feed upon each other, and at once allows itself to fester more easily, and snuffs out the old torches of guidance, people lose themselves infinitely more, get stuck in suboptimalities, find themselves more limited than ever before, ironically (TC)

“Just instinct, explained away” even if true, is it really the case that there is nothing underneath this? Who’s to say that there is a dichotomy here? Does the existence of base instinct negate any notion of goodness? I think not. And even if these moralizing behaviours are the manifestation of some instinct, we must be correct about WHICH instinct; perhaps there is an instinct for individual perception of goodness rather than mere detached “group survival” in a vacuum; that would be more interesting (TC)

Adam and Eve, Homo sapiens is not special on the Bible, only those two (other contemporary humans); story as how God’s gifts can be a double edged sword; obviously we love the idea of free will and of values, but these very things can be our downfall, inherently; disobeying clear divine instructions

Mathematics, project - game theory; maybe try to reformulate the whole field; get away from behaviour at infinity, consider deeply what it means to have an advantage, even cyclical games might confer some hidden advantage; probabilities of good strategies in general even if they are exploitable; given some advantage is there a chain of individually exploitable action that in the end offers freest advantage while limiting response from adversary, how much of the adversary’s action space is pruned by your own strategy, loop in Bayesian stuff to model “generally sensible” strategy models for the sake of probability distributions, etc

Acts 2:4 - the disciples are given the ability to speak different tongues by the Spirit. ability to communicate the Gospel across civilizations and societies.
2:20 - the sun will be turned into darkness, and the moon into blood — interesting; up to this point Peter seems to be describing a vision of destruction and earthly mayhem. The sun turning into darkness could signify the “guiding light” of the world disappearing (which it currently is); there is no more day, and day is clearly meant to be a mode of life in which the light of the Lord is clearly and visibly and perceptibly shining through, and is the period during which his sheep move and act (people work and mostly act during the day), as we read the Bible I am sure there will be more allusions to the allegory of daytime; at this point it is always night, people will not see or feel the Lord; constant darkness means constant night, Jesus said at some point in the Gospel of John that people should not act at night, night meaning an absence of the Lord in the heart, hard and uncertain times; but even at night people have the moon, the Lord emanates his light even then, even if it does not “feel” as the forefront it is there; but even the moon, which is seen as guidance in this darkness, is turned “into blood”; that people will turn to violence, brutality, hatred, other depravity as the way forward in the nighttime which never turns to day
But “whosoever shall call on the name of the Lord shall be saved”. Those who remain moved and directed to the Lord shall prosper, even in this time. “Calling on the name of the Lord” indicates a lens and a motivation; to be motivated by the Way, in one’s beliefs, values, and desired action.
Think of crucifixion of Jesus, and the result of this being the transcendence of death, and that we may be saved; I do not understand fully, and must investigate more; but there is clearly something here, and it applies at many levels. Christ bravely journeyed through the most immense pain, prolonged torture, inflicted by other people; unwavering in his commitment to the Father. The moral of the crucifixion applies on many levels, including several I do not yet see or know;  but for one, when one can withstand immense pain and even the concept of physical death, in their commitment to the Way; one has transcended death. Jesus came back from the dead; pain and death do not have any power over the Way, which is the most powerful force of all. Jesus loved all of his children, so much that he would brave the worst of physical and worldly affliction. A clear demonstration of the love of one another, and the corresponding bravery and self sacrifice for one’s friends (“true love has no greater than this: to lie down one’s life for one’s friends”) as immensely high virtues.
2.26 - “therefore did my heart rejoice, and my tongue was glad” - both internally rejoicing, but also externally and communicatively happy. “Moreover my flesh shall also rest in hope” - physical state aligned with mental, ability to resist temptation; to move in a manner aligned with the Lord, out of hope, and high aesthetic passion and gratitude for the Lord’s power and love, which is higher than what any temptation could offer. In particular this refers to Christ, as never being in Hell, and free from corruption. Never being in hell refers perhaps to never being in some immense spiritual suffering, always looking to the Lord will save one from any such perception, even in times of immense physical torture (link to willpower). But also meaning the soul did not deviate from the way, into any realm of depravity; and correspondingly the flesh was never corrupt.
“Unbecoming generation” - historical movement away from righteousness; we should be on the lookout for a common thread of “socially empowered vice” in the past, it would remain prevalent today
“Those who GLADLY received his word were baptized”. Emphasis on personal alignment and emotion and faith and joy over mere rules. Intention over action in a vacuum 
“Fear came upon every soul” — concept of fear of God, reverence; without this is disobedience, feelings of superiority, disrespect
“Sold their possessions and goods, and parted them among all men” — what is truly important in life? It is not possessions or goods or luxury. Love of friends is greater
“Continuing daily with one accord in the temple” — everyone aligned to Way, and there is only one Way; thus logically, one accord. Notice the temple is the constant setting. God is the lens through which all else shall be seen. Worship as perceiving and being immensely moved by the infinite beauty of the works of the Lord, and to feel immense gratitude and reverence, and thus act accordingly.


Project, programming - use ML classifier model as “security measure”; if user provides correct object; then the model outputs 1, of not it does not grant access. Switch up the ML model randomly. Want ML model to be very restrictive. Only want it to activate for very very specific things

History, religion - does not make sense for Christianity to have spread past the point of “cult” in such an environment rife with opposing prevailing ideas and no natural manipulative draw (unlike Islam etc which thrive in environment with no existing strong opposition, and inherent chaos across the entire group; there is external motivation as draw); best logical explanation is the truth of it; God as the draw

Nietzche - his writing style is incredible.
“Ethical systems as anti natural”… well this is the point. To transcend over animal. “Intelligence” can be considered unnatural, and in many ways has usurped the natural functioning of the human body and brain itself; but it is real, and perhaps is THE ONLY REASON humanity exists in the first place; and who’s to say that “unnatural” or “foolish” (says who? Only under literally arbitrary axioms of value?) heroism, which clearly links to his anathema morality, is the reason we have dominion over other animals and certain forces of nature in the first place. His “lack of morality” itself, as a system (there is always a system), would run us to the ground far more efficiently, effectively, resoundingly, and brutally than any of these established “moral systems” ever could. (Socrates in the republic makes a similar argument). In terms of the “gay science” he will probably preach, I can’t imagine anything more personally jubilant than these heroic ideals that are themselves embedded in us naturally; to eschew them is itself unnatural, and it will show
Allegedly the hero on stage is impactful due to its catering to individuals profoundly moved by the apparently once unforeseen idea that “they are important” or their life has meaning. Nietzsche claimed earlier that it is natural to care so much about the survival of the species, to the point where it embeds itself as the root cause of moral pandering; if it is so natural, how could it be that people lack such ideas in themselves to begin with, and why would they be so drawn to the newest hero, if they already have the purely natural drive to prosper? There is some contradiction is his points
“Every one of these great teachers of reason and morality was vanquished by laughter, reason and nature”… this is simply untrue. Even if all ancient philosophers had some “mistake” in one of their points, meaning the overall philosophy has a flaw and cannot be taken as the whole truth, they have many ideals, points, perhaps even overall direction, that clearly stand the test of time, and in fact agree with each other over time and space.
“Man has to believe, and know, FROM TIME TO TIME, why he exists” — very interesting, good point; people are stuck between some flip flopping between desire for meaning and living everything according to unquestioned nature and habit, unconsciously; without reason or craving for why

Religion, lifestyle - why do we deviate from the Way, why do temptations hold any weight? We feel like other things would provide some extra pleasure; and tell ourselves that it can only be beneficial, and additive, though it never is. But to be satisfied is not merely to be satisfied with some static configuration of items and skills; such things are material objects, and constitute some absolute inertial perspective. “We want more”, we say, and claim this is healthy, philosophically, and absurd to not want anything more. But it misses the point, and views “having” as referring only to the material world. But this is merely a skewed definition; we can equally view from the perspective of motion rather than of static materialism; this is the Way, that the way is good enough; that every day, the way we act is immensely satisfying. This is beyond a material state, it is a state of mind and of alignment. Temptations simply cannot add more to this; to give in and align yourself to temptations is to lose the Way; you end up with LESS than you had before.

Physics - related - inertial frame merely is from the point of view of a constant aspect of a system. The Way is a higher order inertia, from the perspective of action/constant movement and direction (can think in terms of a subspace, that can be carved from the constant/patternistic aspect of the system). Jerk, and discontinuities, break us out of any inertial frame (perhaps send us onto another one), as now there is a fundamental discontinuity, arising from outside of the considered system, that breaks the pattern and constant nature of the view of the system.
That last thought would be incredibly interesting to pursue. Constancy depends on the system and also the “level” of the system in the overarching scheme of super systems. Something appearing discontinuous can be in fact constant on some other level. How far can we take this?

Philosophy - many philosophies have a constant common thread, God in all good things

Psychology, society - negativity, “it won’t work” etc, even if rational and meaningful, people don’t recognize it as such; but it gives others motivation to try and be “heroes”, to manifest the story of acting for good, they are the respected ones, even if they are stupid and act suboptimally, and not those who expose the problems. Even if truly your idea has no negativity, people frame things, and things are relative

Mathematics - “functional limit” and functional bounding (given any two continuous function, is there another (perhaps nontrivial; of “different functional form”) continuous function that always lies between them except perhaps in the limit? (Functional Asymptotes/limits across parameter dimensions).

History, lifestyle - Mozart - always optimistic
Amazing memory and confidence in it, would fill in compositions later, for the sake of deadline optimizations; just draw the main idea and factor in the rest later; meaning he has an amazing mental representation (“compression algorithm”) that gets to the heart of things. Consider for ourselves (practice in notes)
Efficient work sched (5-7h); finish at high pace, mentally figure out before realizing idea

Project - try modeling our own “toy” neural circuit through physical processes
Electrical potential, leading to o external action/Mvmt, ability to effect its own state, long term changes, membranes and cations/anions (for electrical potential), neural conducting and insulating material, different neural scaffoldings (neurotransmitters), instigation of metabolic processes

Music - NEED TO EXPLORE THIS MORE, THIS IS INCOMPLETE
Had a little possible epiphany while playing Bach Prelude in C. This analysis only considers the right hand, so in fact the truth is RICHER than this, but even RH has is significant
Intervals of 3 notes, around a center (left part and right part). Compare based on gap between note and center; analogy to past (left, prior in time) to future or present (right)
Left = right as laxness, left > right as some variation of the past framing the future (either good or bad), left < right as future framing the past. Yearning sensations, anxiety and uncertainty, satisfaction, contemplation, and even laughter/comedy and “comedic uncertainty or absurdity” at the end all factor in. Revisit later in depth

Religion - acts 3
Lame man is healed (significance of RH? Reoccs) 
“Why wonder thee at this?” From realm of miracle and being “shallowly impressed” but by def naive, unexpect; to love of God; if one mirac is impress, wb entire syst? (Manifs daily)
Crucif; they chose murderer and “killed” prince of life, (this is world’s desire); but in reality he is risen up; always there, always powerful even despite worldly appearances and desire; triumph of light over flesh

Philosophy, religion - “what if wrong? Being unwavering os subopt! Can be limiting!” Etc. this is seed of doubt. And if i am deeply satisfied, then need nothing else; notion of greater is absurd! Only discontent under assumption of something greater! My faith is rational, but even if irrational, for aforementioned reasons, it is better to be so called irrational!
Current state of mind, movement, The Way; is immensely great, no dissatisfaction at all; and it is indeed optimal; it IS the Way

AI, project - saw an autonomous smallworld project
Use LLM prompting to describe external state of world at each timestep, communicate it to autonomous agents (different initial prompting of LLMs), they reflect (prompt) and perhaps summairze their state with another prompt (information compression), then another prompt perhaps asking for discrete action (choose a category in which you want to act: visiting, talking, nothing, etc), perhaps follow up question for specificity (who do you want to talk to?), those last two prompts give discrete responses that can be translated to simple code: if walking somewhere, shortest pth algorithm across graphical screen, if talking, walk to them etc.
very cool, but obviously immensely limited, even with idea of memory compression/consolidation: at each step an ungodly amount of processing is done, if you have separate LLMs either they all need to be stored (memory hit) or a few are used in parallel but sequentially serving each actor (time), which limits the world we can generate, either in number of actors, or the fact that stuff only happens or unravels when the user perceives it
Wait i just hit on a very interesting idea… lazy execution, applied to life? If you think about consciousness, this could indeed be the case; only computation we are really aware of is our own…
But even here, as ive been sayin, the link btween LLM and action is illusory;action is done through hacky parsing and is dealt with in the “software” domain through code that is inherently limited.

AI, neuroscience - brain as some kind of circuit that adapts itself.
Electrical signals: super fast
Versus computer vision algorithms (CNN, etc) which are encoded suboptimally on computer hardware compared to the conducting of electricity
Brain’s consciousness is incomplete relative to complete perception of signals; immediate discarding of many components versus NN which always takes everything thru whole process; think about figuring out low relevance (through training); then discarding it at very early stages